---
title: "Hypothesis-Based Results"
output:
  html_document:
    df_print: paged
  pdf_document: default
  html_notebook: default
editor_options:
  chunk_output_type: inline
---

```{r packages,warning=TRUE, include=FALSE}
library("tidyverse")
library("metafor")
library("robumeta")
library("readxl")
library("writexl")
```


```{r data download and subsetting, include=FALSE}
directory = "/Users/renatafayz/Documents/tACS_MetaAnalysis"
mlm.data <- read_excel(paste0(directory, "/Data_for_analysis/Analysis_Hypothesis.xlsx"))

# Performance, RT and clinical datasets

mlm.clin <- mlm.data[mlm.data$population == 'Clinical',]

# uncomment to test w/o clinical studies
#mlm.data <- mlm.data[mlm.data$population != "Clinical",]

mlm.perf <- mlm.data[mlm.data$dv == 'Performance',]
mlm.rt <- mlm.data[mlm.data$dv == 'RT',]
```

## Overall Effect of tACS 

Pool effects using robu() function from robumeta package to compute overall effects for All, Performance, and RT measures

*All* 

```{r overall effect All, echo=FALSE}
model_intercept <- robu(formula = y ~ 1, data = mlm.data, studynum = ID, var.eff.size = v, rho = 0.8, small = FALSE)
print(model_intercept)

sensitivity(model_intercept)
```

*Outliers All*

For identification of outliers use rstudent() function from metafor package (robumeta doesn't have appropriate solution). 

```{r overall effect All (outliers removed), echo=FALSE}

model_rma <- rma.uni(y, v, weights = model_intercept$data.full$r.weights, data=mlm.data)
rstud <- rstudent(model_rma)
outliers <- model_intercept$data$experiment[abs(rstud$z) >= 1.96]
if(sum(abs(rstud$z) >= 1.96) !=0) {
  model_out <- robu(formula = y ~ 1, data = mlm.data[abs(rstud$z)<1.96,], studynum = ID, var.eff.size = v, rho = .8, small = FALSE)
}
print(outliers)
print(model_out)

```

*Performance*

```{r overall effect Performance, echo=FALSE}
model_intercept <- robu(formula = y ~ 1, data = mlm.perf, studynum = ID, var.eff.size = v, rho = 0.8, small = FALSE)
print(model_intercept)

sensitivity(model_intercept)
```

*Outliers Performance*

```{r overall effect Performance (outliers removed), echo=FALSE}

model_rma <- rma.uni(y, v, weights = model_intercept$data.full$r.weights, data=mlm.perf)
rstud <- rstudent(model_rma)
outliers <- model_intercept$data$experiment[abs(rstud$z) >= 1.96]
if(sum(abs(rstud$z) >= 1.96) !=0) {
  model_out <- robu(formula = y ~ 1, data = mlm.perf[abs(rstud$z)<1.96,], studynum = ID, var.eff.size = v, rho = .8, small = FALSE)
}
print(outliers)
print(model_out)

```

*Reaction Time*

```{r overall effect RT, echo=FALSE}
model_intercept <- robu(formula = y ~ 1, data = mlm.rt, studynum = ID, var.eff.size = v, rho =.8, small = TRUE)
print(model_intercept)

sensitivity(model_intercept)
```

*Outliers RT*

```{r overall effect RT (outliers removed), echo=FALSE}

model_rma <- rma.uni(y, v, weights = model_intercept$data.full$r.weights, data=mlm.rt)
rstud <- rstudent(model_rma)
outliers <- model_intercept$data$experiment[abs(rstud$z) >= 1.96]
if(sum(abs(rstud$z) >= 1.96) !=0) {
  model_out <- robu(formula = y ~ 1, data = mlm.rt[abs(rstud$z)<1.96,], studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
}
print(outliers)
print(model_out)

```

## Overall Effects of tACS by Domains 

*Domains | All* 

```{r domains All, echo=FALSE}
# Fit RVE intercept model

domains = c("Working Memory", "Long-Term Memory", "Attention", "Executive Control", "Intelligence", "Motor Learning", "Motor Memory", "Learning", "Decision-Making")

effects_robu = data.frame(matrix(ncol = 9, nrow = 8))
model = list()

for(d in 1:length(domains)) {
  # fit RVE model for each domain 
  model[[d]] <- robu(formula = y ~ 1, 
                        data = mlm.data[mlm.data$domain==domains[d],],
                        studynum = ID, 
                        var.eff.size = v, 
                        rho = .8, 
                        small = TRUE)
  # extract data from the model
  effects_robu[d] <- c(model[[d]]$reg_table$b.r,   # effect size
                       model[[d]]$reg_table$prob,  # p-value
                       model[[d]]$reg_table$CI.L,  # CI lower bound
                       model[[d]]$reg_table$CI.U,  # CI upper bound
                       model[[d]]$mod_info$I.2[1], # I squared
                       model[[d]]$reg_table$dfs,   # degrees of freedom
                       model[[d]]$N,               # number of studies (N)
                       model[[d]]$M)               # number of effects (k)
}

colnames(effects_robu) <- domains
rownames(effects_robu) <- c('es', 'pval', 'ci_lb', 'ci_up', 'I^2', 'df', 'N', 'k')

# transpose
effects_robu <- as.data.frame(t(as.matrix(effects_robu)))
print(effects_robu)
# save as csv 
write_csv(effects_robu, paste0(directory,"/Results/Domains_All_hypo.csv"))

```

*Domains | Performance* 

```{r domains Performance, echo=FALSE}
# Fit RVE intercept model

effects_robu = data.frame(matrix(ncol = 9, nrow = 8))
model = list()

for(d in 1:length(domains)) {
  model[[d]] <- robu(formula = y ~ 1, 
                        data = mlm.perf[mlm.perf$domain==domains[d],],
                        studynum = ID, 
                        var.eff.size = v, 
                        rho = .8, 
                        small = TRUE)
  effects_robu[d] <- c(model[[d]]$reg_table$b.r,
                       model[[d]]$reg_table$prob,
                       model[[d]]$reg_table$CI.L,
                       model[[d]]$reg_table$CI.U,
                       model[[d]]$mod_info$I.2[1],
                       model[[d]]$reg_table$dfs,
                       model[[d]]$N,
                       model[[d]]$M)
}

colnames(effects_robu) <- domains
rownames(effects_robu) <- c('es', 'pval', 'ci_lb', 'ci_up', 'I^2', 'df', 'N', 'k')

# transpose
effects_robu <- as.data.frame(t(as.matrix(effects_robu)))
print(effects_robu)

write_csv(effects_robu, paste0(directory, "/Results/Domains_Perf_hypo.csv"))

```

*Domains | RT* 

```{r domains RT, echo=FALSE}
# remove domains Long-Term Memory, Motor Learning and Learning (each has 1 study), and Decision-Making (0 studies)  

domains = c("Working Memory", "Attention", "Executive Control", "Intelligence", "Motor Memory")
  
effects_robu = data.frame(matrix(ncol = 5, nrow = 8))
model = list()

for(d in 1:length(domains)) {
  model[[d]] <- robu(formula = y ~ 1, 
                        data = mlm.rt[mlm.rt$domain==domains[d],],
                        studynum = ID, 
                        var.eff.size = v, 
                        rho = .8, 
                        small = TRUE)
  effects_robu[d] <- c(model[[d]]$reg_table$b.r,
                       model[[d]]$reg_table$prob,
                       model[[d]]$reg_table$CI.L,
                       model[[d]]$reg_table$CI.U,
                       model[[d]]$mod_info$I.2[1],
                       model[[d]]$reg_table$dfs,
                       model[[d]]$N,
                       model[[d]]$M)
}

colnames(effects_robu) <- domains
row.names(effects_robu) <- c('es', 'pval', 'ci_lb', 'ci_up', 'I^2', 'df', 'N', 'k')

# transpose
effects_robu <- as.data.frame(t(as.matrix(effects_robu)))
print(effects_robu)

write_csv(effects_robu, paste0(directory,"/Results/Domains_RT_hypo.csv"))
```

## Subgroup: Older Adults 

*Older Adults | All*
```{r older adults All, echo=FALSE}
model_elderly <- robu(formula = y ~ 1, data= subset(mlm.data, population=="elderly", ), studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
print(model_elderly)
sensitivity(model_elderly)
```

*Older Adults | Performance*
```{r older adults Performance, echo=FALSE}
model_elderly <- robu(formula = y ~ 1, data= subset(mlm.perf, population=="elderly"), studynum = ID,  var.eff.size = v, rho = .8, small = TRUE)
print(model_elderly)
sensitivity(model_elderly)
```

*Older Adults | RT*
```{r older adults RT, echo=FALSE}
model_elderly <- robu(formula = y ~ 1, data= subset(mlm.rt, population=="elderly"), studynum = ID, var.eff.size = v, rho = .8, small = TRUE)
print(model_elderly)
sensitivity(model_elderly)
```
